When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-01-19 06_Paper/COG-ED/Stage 1/Manuscript.tex

>>>>

\hypertarget{supplement}{%
\section{Supplement}\label{supplement}}

\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{0}

\hypertarget{results-of-the-pilot-study}{%
\subsection{Results of the pilot study}\label{results-of-the-pilot-study}}

\hypertarget{hypothesis-1a-the-signal-detection-measure-d-declines-with-increasing-n-back-level.}{%
\subsection{Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.}\label{hypothesis-1a-the-signal-detection-measure-d-declines-with-increasing-n-back-level.}}

ANOVA:

\(F(2.30, 32.20) = 0.00\), \(p > .999\), \(\eta_{p}^{2}=\) 2.16e-32, 95\%~CI {[}0.00, 1.00{]}, \(BF10=\) 0.09

\hypertarget{hypothesis-1b-reaction-time-increases-with-increasing-n-back-level.}{%
\subsection{Hypothesis 1b: Reaction time increases with increasing n-back level.}\label{hypothesis-1b-reaction-time-increases-with-increasing-n-back-level.}}

ANOVA:

\(F(2.14, 30.00) = 17.18\), \(p < .001\), \(\eta_{p}^{2}=\) 0.55, 95\%~CI {[}0.33, 1.00{]}, \(BF10=\) 125.61

Paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-1}Paired contrasts for the rmANOVA comparing reaction time between n-back levels}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -0.14 & 0.03 & 42.00 & -4.15 & 0.001 & 249.00 & 0.29 & {}[0.11, 1.00]\\
1 - 3 & -0.24 & 0.03 & 42.00 & -7.00 & 0.000 & 994.00 & 0.54 & {}[0.36, 1.00]\\
1 - 4 & -0.16 & 0.03 & 42.00 & -4.86 & 0.000 & 27.90 & 0.36 & {}[0.17, 1.00]\\
2 - 3 & -0.10 & 0.03 & 42.00 & -2.85 & 0.033 & 5.94 & 0.16 & {}[0.03, 1.00]\\
2 - 4 & -0.02 & 0.03 & 42.00 & -0.72 & 0.891 & 0.32 & 0.01 & {}[0.00, 1.00]\\
3 - 4 & 0.07 & 0.03 & 42.00 & 2.14 & 0.158 & 4.41 & 0.10 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\hypertarget{hypothesis-1c-ratings-on-all-nasa-tlx-dimensions-increase-with-increasing-n-back-level.}{%
\subsection{Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.}\label{hypothesis-1c-ratings-on-all-nasa-tlx-dimensions-increase-with-increasing-n-back-level.}}

Mental subscale ANOVA:

\(F(2.08, 27.03) = 69.96\), \(p < .001\), \(\eta_{p}^{2}=\) 0.84, 95\%~CI {[}0.74, 1.00{]}, \(BF10=\) 240,305,851.21

Mental subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-2}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -4.43 & 0.80 & 39.00 & -5.53 & <.001 & 1,400.00 & 0.44 & {}[0.25, 1.00]\\
1 - 3 & -8.43 & 0.80 & 39.00 & -10.50 & <.001 & 35,700.00 & 0.74 & {}[0.62, 1.00]\\
1 - 4 & -10.80 & 0.80 & 39.00 & -13.50 & <.001 & 190,000.00 & 0.82 & {}[0.74, 1.00]\\
2 - 3 & -4.00 & 0.80 & 39.00 & -5.00 & <.001 & 373.00 & 0.39 & {}[0.20, 1.00]\\
2 - 4 & -6.36 & 0.80 & 39.00 & -7.94 & <.001 & 3,330.00 & 0.62 & {}[0.45, 1.00]\\
3 - 4 & -2.36 & 0.80 & 39.00 & -2.94 & 0.027 & 38.10 & 0.18 & {}[0.04, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Physical subscale ANOVA:

\(F(1.61, 20.96) = 7.86\), \(p = .005\), \(\eta_{p}^{2}=\) 0.38, 95\%~CI {[}0.10, 1.00{]}, \(BF10=\) 0.34

Physical subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-3}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -1.64 & 0.80 & 39.00 & -2.06 & 0.185 & 3.51 & 0.10 & {}[0.00, 1.00]\\
1 - 3 & -3.07 & 0.80 & 39.00 & -3.85 & 0.002 & 6.50 & 0.28 & {}[0.10, 1.00]\\
1 - 4 & -3.50 & 0.80 & 39.00 & -4.38 & <.001 & 7.66 & 0.33 & {}[0.14, 1.00]\\
2 - 3 & -1.43 & 0.80 & 39.00 & -1.79 & 0.294 & 1.79 & 0.08 & {}[0.00, 1.00]\\
2 - 4 & -1.86 & 0.80 & 39.00 & -2.33 & 0.110 & 2.00 & 0.12 & {}[0.01, 1.00]\\
3 - 4 & -0.43 & 0.80 & 39.00 & -0.54 & 0.950 & 0.38 & 7.33e-03 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Time subscale ANOVA:

\(F(2.14, 27.86) = 31.25\), \(p < .001\), \(\eta_{p}^{2}=\) 0.71, 95\%~CI {[}0.53, 1.00{]}, \(BF10=\) 24.80

Time subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -1.64 & 0.82 & 39.00 & -2.00 & 0.206 & 11.40 & 0.09 & {}[0.00, 1.00]\\
1 - 3 & -5.14 & 0.82 & 39.00 & -6.26 & <.001 & 278.00 & 0.50 & {}[0.31, 1.00]\\
1 - 4 & -7.14 & 0.82 & 39.00 & -8.69 & <.001 & 3,710.00 & 0.66 & {}[0.51, 1.00]\\
2 - 3 & -3.50 & 0.82 & 39.00 & -4.26 & 0.001 & 38.80 & 0.32 & {}[0.13, 1.00]\\
2 - 4 & -5.50 & 0.82 & 39.00 & -6.69 & <.001 & 1,060.00 & 0.53 & {}[0.35, 1.00]\\
3 - 4 & -2.00 & 0.82 & 39.00 & -2.43 & 0.087 & 3.09 & 0.13 & {}[0.01, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Performance subscale ANOVA:

\(F(2.12, 27.59) = 6.78\), \(p = .004\), \(\eta_{p}^{2}=\) 0.34, 95\%~CI {[}0.09, 1.00{]}, \(BF10=\) 1.82

Performance subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & 1.50 & 1.10 & 39.00 & 1.37 & 0.526 & 1.00 & 0.05 & {}[0.00, 1.00]\\
1 - 3 & 3.93 & 1.10 & 39.00 & 3.59 & 0.005 & 33.70 & 0.25 & {}[0.08, 1.00]\\
1 - 4 & 4.21 & 1.10 & 39.00 & 3.85 & 0.002 & 5.32 & 0.28 & {}[0.10, 1.00]\\
2 - 3 & 2.43 & 1.10 & 39.00 & 2.22 & 0.136 & 11.00 & 0.11 & {}[0.01, 1.00]\\
2 - 4 & 2.71 & 1.10 & 39.00 & 2.48 & 0.079 & 1.83 & 0.14 & {}[0.01, 1.00]\\
3 - 4 & 0.29 & 1.10 & 39.00 & 0.26 & 0.994 & 0.28 & 1.74e-03 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Effort subscale ANOVA:

\(F(1.57, 20.43) = 28.65\), \(p < .001\), \(\eta_{p}^{2}=\) 0.69, 95\%~CI {[}0.47, 1.00{]}, \(BF10=\) 10,733.57

Effort subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -2.71 & 0.96 & 39.00 & -2.84 & 0.035 & 1,020.00 & 0.17 & {}[0.03, 1.00]\\
1 - 3 & -6.79 & 0.96 & 39.00 & -7.09 & <.001 & 774.00 & 0.56 & {}[0.39, 1.00]\\
1 - 4 & -7.79 & 0.96 & 39.00 & -8.14 & <.001 & 1,380.00 & 0.63 & {}[0.47, 1.00]\\
2 - 3 & -4.07 & 0.96 & 39.00 & -4.26 & 0.001 & 55.60 & 0.32 & {}[0.13, 1.00]\\
2 - 4 & -5.07 & 0.96 & 39.00 & -5.30 & <.001 & 44.60 & 0.42 & {}[0.22, 1.00]\\
3 - 4 & -1.00 & 0.96 & 39.00 & -1.05 & 0.724 & 0.62 & 0.03 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Frustration subscale ANOVA:

\(F(2.53, 32.94) = 35.31\), \(p < .001\), \(\eta_{p}^{2}=\) 0.73, 95\%~CI {[}0.58, 1.00{]}, \(BF10=\) 17,679.16

Frustration subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -1.57 & 0.91 & 39.00 & -1.73 & 0.323 & 3.52 & 0.07 & {}[0.00, 1.00]\\
1 - 3 & -5.71 & 0.91 & 39.00 & -6.28 & <.001 & 590.00 & 0.50 & {}[0.32, 1.00]\\
1 - 4 & -8.36 & 0.91 & 39.00 & -9.19 & <.001 & 27,000.00 & 0.68 & {}[0.54, 1.00]\\
2 - 3 & -4.14 & 0.91 & 39.00 & -4.56 & <.001 & 71.10 & 0.35 & {}[0.16, 1.00]\\
2 - 4 & -6.79 & 0.91 & 39.00 & -7.46 & <.001 & 2,660.00 & 0.59 & {}[0.42, 1.00]\\
3 - 4 & -2.64 & 0.91 & 39.00 & -2.91 & 0.029 & 2.54 & 0.18 & {}[0.03, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\hypertarget{hypothesis-2a-subjective-values-decline-with-increasing-n-back-level.}{%
\subsection{Hypothesis 2a: Subjective values decline with increasing n-back level.}\label{hypothesis-2a-subjective-values-decline-with-increasing-n-back-level.}}

ANOVA:

\(F(1.80, 25.26) = 7.80\), \(p = .003\), \(\eta_{p}^{2}=\) 0.36, 95\%~CI {[}0.10, 1.00{]}

Contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-8}Different contrasts for the rmANOVA comparing subjective values between n-back levels}

\begin{tabular}{llllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
Declining Linear & 1.06 & 0.22 & 42.00 & 4.78 & <.001 & 0.35 & {}[0.17, 1.00]\\
Ascending Quadratic & 0.07 & 0.10 & 42.00 & 0.72 & 0.475 & 0.01 & {}[0.00, 1.00]\\
Declining Logistic & 1.16 & 0.25 & 42.00 & 4.56 & <.001 & 0.33 & {}[0.15, 1.00]\\
Positively Skewed Normal & 0.66 & 0.16 & 42.00 & 4.21 & <.001 & 0.30 & {}[0.12, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\hypertarget{hypothesis-2b-subjective-values-decline-with-increasing-n-back-level-even-after-controlling-for-declining-task-performance-measured-by-signal-detection-d-and-reaction-time.}{%
\subsection{Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d' and reaction time.}\label{hypothesis-2b-subjective-values-decline-with-increasing-n-back-level-even-after-controlling-for-declining-task-performance-measured-by-signal-detection-d-and-reaction-time.}}

Multi level model:

\begin{table}

\caption{\label{tab:unnamed-chunk-9}Effects of n-back load level on subjective value controlled 
    for task performance (d' and reaction time).}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrr}
\toprule
Parameter & Beta & $SE$ & $p$-value & Random Effects (SD)\\
\midrule
\cellcolor{gray!6}{Intercept} & \cellcolor{gray!6}{0.81} & \cellcolor{gray!6}{0.03} & \cellcolor{gray!6}{<.001***} & \cellcolor{gray!6}{0.09}\\
$N$-back level & -0.12 & 0.04 & 0.003** & 0.12\\
\cellcolor{gray!6}{d'} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.238} & \cellcolor{gray!6}{}\\
median RT & 0.25 & 0.19 & 0.21 & \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{Note: } 
\item NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.
\end{tablenotes}
\end{threeparttable}
\end{table}

The intraclass correlation equals 0.015.

The Bayes Factor \(BF10\) of the multi level model approached infinity.

The conditional \(R^2\) of the model describes the proportion of variance explained by both fixed and random effects, and is \(R^2=\) 0.74.

The effect size is \(f^2=\) -0.075.

\hypertarget{hypothesis-3a-participants-with-high-nfc-scores-have-higher-subjective-values-for-2--and-3-back-but-lower-subjective-values-for-1-back-than-participants-with-low-nfc-scores.}{%
\subsection{Hypothesis 3a: Participants with high NFC scores have higher subjective values for 2- and 3-back but lower subjective values for 1-back than participants with low NFC scores.}\label{hypothesis-3a-participants-with-high-nfc-scores-have-higher-subjective-values-for-2--and-3-back-but-lower-subjective-values-for-1-back-than-participants-with-low-nfc-scores.}}

ANOVA:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-10}Main effects and interaction of NFC group and n-back level on subjective values}

\footnotesize{

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{Sum Sq} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{error Sum Sq} & \multicolumn{1}{c}{error $df$} & \multicolumn{1}{c}{$F$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
Intercept & 0.52 & 1.00 & 0.71 & 13.00 & 9.41 & 0.009 & 0.42 & {}[0.09, 1.00]\\
NFC group & 0.00 & 1.00 & 0.71 & 13.00 & 0.01 & 0.931 & 5.96e-04 & {}[0.00, 1.00]\\
n-back level & 0.04 & 2.00 & 1.66 & 26.00 & 0.32 & 0.726 & 0.02 & {}[0.00, 1.00]\\
NFC group x n-back level & 0.02 & 2.00 & 1.66 & 26.00 & 0.19 & 0.829 & 0.01 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\hypertarget{hypothesis-3b-participants-with-high-nfc-scores-have-lower-nasa-tlx-scores-in-every-n-back-level-than-participants-with-low-nfc-scores.}{%
\subsection{Hypothesis 3b: Participants with high NFC scores have lower NASA-TLX scores in every n-back level than participants with low NFC scores.}\label{hypothesis-3b-participants-with-high-nfc-scores-have-lower-nasa-tlx-scores-in-every-n-back-level-than-participants-with-low-nfc-scores.}}

ANOVA:

Main effect of the NFC group:

\(F(1, 12) = 7.57\), \(p = .018\), \(\hat{\eta}^2_G = .348\), 90\% CI \([.030, .610]\), \(BF10=\) 88

Main effect of the n-back level:

\(F(1.56, 18.71) = 68.33\), \(p < .001\), \(\hat{\eta}^2_G = .466\), 90\% CI \([.239, .603]\), \(BF10=\) 1000

Interaction effect of NFC group and n-back level:

\(F(1.56, 18.71) = 0.84\), \(p = .422\), \(\hat{\eta}^2_G = .011\), 90\% CI \([.000, .008]\), \(BF10=\) 3398060

Paired contrasts for the main effect of n-back level:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-11}Main effects and interaction of NFC group and n-back level on NASA-TLX scores}

\footnotesize{

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{Sum Sq} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{error Sum Sq} & \multicolumn{1}{c}{error $df$} & \multicolumn{1}{c}{$F$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
Intercept & 5,770.00 & 1.00 & 241.00 & 12.00 & 287.00 & <.001 & 0.96 & {}[0.91, 1.00]\\
NFC group & 152.00 & 1.00 & 241.00 & 12.00 & 7.57 & 0.018 & 0.39 & {}[0.05, 1.00]\\
n-back level & 249.00 & 3.00 & 43.70 & 36.00 & 68.30 & <.001 & 0.85 & {}[0.77, 1.00]\\
NFC group x n-back level & 3.04 & 3.00 & 43.70 & 36.00 & 0.84 & 0.483 & 0.07 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}
